---
title: "Relationship between NTD USD exchange rate and Taiwan Stock market performance"
author: "Yi-Fang Lo"
date: "7/11/2019"
output: html_document
---
# Data about Taiwan Stock Market Index and Exchange rate
First inport the data about exchange rate and call out dplyr 
[source](https://www.taifex.com.tw/cht/3/dailyFXRate)

```{r}
library(readr)
exchangerate <- read_csv("C:/Users/Maple/Downloads/exchangerate.csv", 
col_types = cols(date = col_date(format = "%m/%d/%Y")))
head(exchangerate)
library(dplyr)
```
Than inport the data about stock market index
[source](https://www.twse.com.tw/zh/page/trading/indices/MI_5MINS_HIST.html)
```{r}
MI_5MINS_HIST <- read_csv("C:/Users/Maple/Downloads/TSI/MI_5MINS_HIST.csv", 
col_types = cols(date = col_date(format = "%m/%d/%Y")))
head(MI_5MINS_HIST)
```

Merge the two sets of data by the parameter "date"
```{r}
data_merged<-merge(exchangerate, MI_5MINS_HIST, by="date")
head(data_merged)
```
Create a new column "median" to represent the overall stock market index
```{r}
data_merged<-data_merged %>% mutate(MEDIAN= max/2+min/2)
head(data_merged)
```
Take out columns "USDNTD" "date" "NEDIAN"
```{r}
data_nece <- data_merged %>% select(date, MEDIAN, USDNTD)
head(data_nece)
```
make a graph based on the data with x=date y= median and usdntd respectively
```{r}
library(tidyverse)
ggplot(data=data_nece)+geom_smooth(mapping=aes(x=date,y=MEDIAN))
```
```{r}
ggplot(data=data_nece)+geom_smooth(mapping=aes(x=date, y=USDNTD))
```

Conclusion 
These is little, if any, relationship between the US NTD exchange rate and Taiwan Stock market index
