---
title: "Exchange rates and stock market"
author: "Yi-Fang Lo"
date: "7/15/2019"
output: html_document
---
# Foreign currencies and Taiwan Stock market

## Objective: explore the relationship between Foreign currency exchange rates and Taiwan stock market performance
## Data source:Previous homework, Click [HERE](https://vladislav292.github.io/2019summer-datasciece/work2/work2.html) to learn more
```{r message=FALSE,warning=FALSE}
library(readr)
library(tidyverse)
data_merged <- read_csv("C:/Users/Maple/Documents/work3/data_merged.csv")

```
## USD exchange rate
First make a graph to visulaize the relationship between date and USD/NTD exchange rate
```{r message=FALSE,warning=FALSE}
ggplot(data = data_merged) + geom_line (mapping = aes (x= date, y=USDNTD))+ geom_point(mapping = aes (x=date, y=USDNTD))

```

Then make a graph to visulaize the relationship between date and Taiwan Stock Market Index

```{r message=FALSE, warning=FALSE}
ggplot(data = data_merged, mapping=aes(x= date, y = MEDIAN)) + geom_line()+geom_point()
```


Make a graph between USD/NTD exchnage rate and Taiwan Stock Index
```{r message=FALSE,warning=FALSE}
ggplot(data = data_merged,mapping = aes(x= USDNTD, y=MEDIAN))+ geom_smooth()+ geom_point()
```

## RMB exchange rate
Make a graph to understade the relationship between date and RMB/NTD exchange rate
```{r message=FALSE,warning=FALSE}
ggplot(data = data_merged,mapping=aes(x=date,y=RMBNTD))+geom_point()+geom_line()
```


And then Make a graph base on RMB and Stock Martet Index

```{r message=FALSE,warning=FALSE}
ggplot(data = data_merged, mapping = aes (x = RMBNTD, y = MEDIAN)) + geom_smooth()+ geom_point()
```
## JPY exchange rate

Make a graph based on JPY/NTD and date, however, since we don't have JPY/NTD exchange rate, thus, we must calculate the value through USD/NTD exchange rate and USD/JPY exchange rate
```{r message=FALSE,warning=FALSE}
data_new <- data_merged %>% mutate(JPYNTD = USDNTD/USDJPY)
```

After we aquire the exchange rate,plot the date-JPY graph

```{r message=FALSE,warning=FALSE}
ggplot(data = data_new, mapping = aes (x= date , y=JPYNTD))+ geom_line()+geom_point()

```


Make a graph to visualize the relation between JPY/NTD and Taiwan Stock Index
```{r message=FALSE,warning=FALSE}
ggplot(data = data_new, mapping = aes(x= JPYNTD, y= MEDIAN))+ geom_point()+ geom_smooth()
```


Lastly, let us do some statistics about currency exchange rates
```{r message=FALSE,warning=FALSE}
USD <- data_new %>%　select(USDNTD)
JPY <- data_new %>%  select(JPYNTD)
RMB <- data_new %>%  select(RMBNTD)
dfUSD <- USD %>% mutate(type="USD")
dfJPY <- JPY %>% mutate(type="JPY")
dfRMB <- RMB %>% mutate(type="RMB")
ggplot(data = dfUSD,mapping = aes(x=type,y=USDNTD))+ geom_boxplot()
ggplot(data = dfJPY,mapping = aes(x=type,y=JPYNTD))+ geom_boxplot()
ggplot(data = dfRMB,mapping = aes(x=type,y=RMBNTD))+ geom_boxplot()
```


## Conclusions
According to these little data we have, we may guess that
* As USD/NTD>30.5, the Stock Market Index becomes really hard to predict and may drop suddenly as USD/NTD>30.75.<br/>
* As RMB/NTD>4.5, the Stock Market Indext has a good chance to be higher than 10250. However, as RMB/NTD<4.5, the chance for the Index to be lower than 10000 is greater than that of be higher than 10000.<br/>
* JPY/NTD exchange rate has little relationship with the Index.<br/>